Occurrence and transmission potential of asymptomatic and pre-symptomatic SARS-CoV-2 infections: a living systematic review and meta-analysis

### 2021-10-29 Manuscript_draft.Rmd
Update Manuscript_draft.Rmd

L1$label <- "Value"
for (i in 1:nrow(L1)) {
  if (L1$model[i] == "q3_pp_m_1") {
  L1$label[i] <- paste(L1$author_1[i], " [", L1$q3_setting_1[i], "]", sep = "")
  }else{
    L1$label[i] <- paste(L1$author_1[i], " [", L1$q3_setting_2[i], "]", sep = "")
  }

}
L1$label2 <- paste(L1$author_1, " [", substrRight(L1$model, 1), "]", sep = "")

@@

L2$label2 <- paste(L2$author_1, " [", substrRight(L2$model, 1), "]", sep = "")
L2$label <- "Value"
for (i in 1:nrow(L2)) {
  if (L2$model[i] == "q3_pp_l_1") {
  L2$label[i] <- paste(L2$author_1[i], " [", L2$q3_setting_1[i], "]", sep = "")
  }else{
    L2$label[i] <- paste(L2$author_1[i], " [", L2$q3_setting_2[i], "]", sep = "")
  }

}

@@

L3$label <- "Value"
i = 1
for (i in 1:nrow(L3)) {
  if (L3$model[i] == "q3_pp_u_1") {
  L3$label[i] <- paste(L3$author_1[i], " [", L3$q3_setting_1[i], "]", sep = "")
  }else{
    L3$label[i] <- paste(L3$author_1[i], " [", L3$q3_setting_2[i], "]", sep = "")
  }

}

>>>>

L1$label <- "Value"
for (i in 1:nrow(L1)) {
  if (L1$model[i] == "q3_pp_m_1") {
    sett <- L1$q3_setting_1[i]
  }else{
    sett <- L1$q3_setting_2[i]
  }
    L1$label[i] <- paste(L1$author_1[i], " [", sett, "]", sep = "")
  }
L1$label2 <- paste(L1$author_1, " [", substrRight(L1$model, 1), "]", sep = "")

@@

L2$label2 <- paste(L2$author_1, " [", substrRight(L2$model, 1), "]", sep = "")
L2$label <- "Value"
i = 1
for (i in 1:nrow(L2)) {
  if (L2$model[i] == "q3_pp_l_1") {
    sett -> L2$q3_setting_1[i]
  }else{
    sett -> L2$q3_setting_2[i]
  }
  L2$label[i] <- paste(L2$author_1[i], " [", sett, "]", sep = "")
}

@@

L3$label <- "Value"
i = 1
for (i in 1:nrow(L3)) {
  if (L3$model[i] == "q3_pp_u_1") {
    sett -> L3$q3_setting_1[i]
  }else{
    sett -> L3$q3_setting_2[i]
  }
  L3$label[i] <- paste(L3$author_1[i], " [", sett, "]", sep = "")
}
